A tutorial on the model-dependent analysis of neutron and X-ray reflectometry

### 2020-07-06 refl_maths/paper.tex
add tim and andrew to author list

\author{Andrew R. McCluskey}
  \email{andrew.mccluskey@diamond.ac.uk}
  \email{a.r.mccluskey@bath.ac.uk}
  \affiliation{Diamond Light Source, Rutherford Appleton Laboratory, Harwell Science and Innovation Campus, Didcot, OX11 0DE, UK}
  \affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath BA2 7AY, UK}

@@

\section*{Acknowledgements}
ARM is supported by the Ada Lovelace Centre – a joint initiative between the Science and Technology Facilities Council (as part of UK Research and Innovation), Diamond Light Source, and the UK Atomic Energy Authority.

>>>>

\author{Andrew R. McCluskey}
  \email{andrew.mccluskey@diamond.ac.uk}
  \email{a.r.mccluskey@bath.ac.uk}
  \affiliation{Diamond Light Source, Rutherford Appleton Laboratory, Harwell Science and Innovation Campus, Didcot, OX11 0DE, UK}
  \affiliation{Department of Chemistry, University of Bath, Claverton Down, Bath BA2 7AY, UK}
\author{Andrew R. J. Nelson}
  \affiliation{Bragg Institute, Australian Nuclear Science and Technology Organisation, Locked Bag 2001, Kirrawee DC, NSW 2232, Australia}
\author{Tim Snow}
  \affiliation{Diamond Light Source, Rutherford Appleton Laboratory, Harwell Science and Innovation Campus, Didcot, OX11 0DE, UK}
  \affiliation{School of Chemistry, University of Bristol, Bristol, BS8 1TS, UK}

@@

\section*{Acknowledgements}
ARM is supported by the Ada Lovelace Centre – a joint initiative between the Science and Technology Facilities Council (as part of UK Research and Innovation), Diamond Light Source, and the UK Atomic Energy Authority.
The authors would like to thank Luke Clifton of ISIS Neutron and Muon Source for insightful input on the manuscript.
